Spatial variation of the native colon microbiota in healthy adults

### 2018-07-17 submission/manuscript.tex
cleaned up repo

Words: 259/260

@@

In addition to identifying features that are specific to each side of
the gut, the ability of the Random Forest to classify samples can serve
as a proxy for similarity. That is, a higher AUC value indicates the
samples are more efficiently classfied (and thus more different) than a
model with a lower AUC value. For instance, the model separating the
proximal and distal mucosa had an AUC of 0.850 whereas the model for
classifying the proximal and distal lumen had a much lower AUC of 0.580.
Further, the latter model required 44 OTUs to best separate the samples
whereas the models separating the mucosa only needed 10 OTUs. The much
lower AUC and need for a high number of features compared to other
models suggest these locations are the most similar of the comparisons
tested. We speculate that the model was less effective at classifying
the proximal and distal luminal contents because the mucosal
microenvironments have more variable selective pressure along the colon
than the luminal microenvironments.

>>>>

Words: 233/250

@@

In addition to identifying features that are specific to each side of
the gut, the ability of the Random Forest to classify samples can serve
as a proxy for similarity. That is, a higher AUC value indicates the
samples are more efficiently classfied (and thus more different) than a
model with a lower AUC value. For instance, the model separating the
proximal and distal mucosa had an AUC of 0.808 whereas the model for
classifying the proximal and distal lumen had a much lower AUC of 0.599.
Further, the latter model required 44 OTUs to best separate the samples
whereas the models separating the mucosa only needed 10 OTUs. The much
lower AUC and need for a high number of features compared to other
models suggest these locations are the most similar of the comparisons
tested. We speculate that the model was less effective at classifying
the proximal and distal luminal contents because the mucosal
microenvironments have more variable selective pressure along the colon
than the luminal microenvironments.
